Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-08-25 writing/CONUS_AOD.qmd
Correct reporting of time difference.

After collocation there were `r scales::comma(nrow(dt))` matched AOD retrievals from `r uniqueN(dt$site)` AERONET sites in CONUS. The quartiles of the absolute difference from the labeled overpass time (one per 1200-km wide tile) and the time of the matched AERONET observation were `r tqs = round(quantile(dt[, abs(as.numeric(difftime(units = "secs", time.sat, time.ground)))], c(.25, .5, .75))); tqs["25%"]` s, `r tqs["25%"]` s, and `r tqs["75%"]` s. While the distribution of AOD is skewed, our estimate of retrieval error and the dependent variable for our predictive model, *diff~AOD~*, was fairly symmetric and Gaussian.

>>>>

After collocation there were `r scales::comma(nrow(dt))` matched AOD retrievals from `r uniqueN(dt$site)` AERONET sites in CONUS. The quartiles of the absolute difference from the labeled overpass time (one per 1200-km wide tile) and the time of the matched AERONET observation were `r tqs = round(quantile(dt[, abs(as.numeric(difftime(units = "secs", time.sat, time.ground)))], c(.25, .5, .75))); tqs["25%"]` s, `r tqs["50%"]` s, and `r tqs["75%"]` s. While the distribution of AOD is skewed, our estimate of retrieval error and the dependent variable for our predictive model, *diff~AOD~*, was fairly symmetric and Gaussian.
